---
title: "Ufoma's_r_task"
author: "Ufoma"
date: "12/27/2021"
output: pdf_document
---


Data Description
Loading Packages
```{r}
library(tidyverse)
library(factoextra)
library(cluster)
library(e1071)
library(rpart)
```

Importing csv file
```{r}
car_sales <- read_csv("Car_sale_ads.csv")
```
Explore dataset
```{r}
glimpse(car_sales)
```
```{r}
str(car_sales)
```

Creating a dataframe from the dataset
```{r}
car_sales <- data.frame(car_sales, stringsAsFactors = FALSE)

```

Converting datatypes
```{r}
#character to factor
car_sales[sapply(car_sales, is.character)] <- lapply(car_sales[sapply(car_sales,
                                              is.character)], as.factor)

#doubles to intergers
car_sales[sapply(car_sales, is.double)] <- lapply(car_sales[sapply(car_sales,
                                              is.double)], as.integer)
```


Checking for missing data
```{r}
colSums(is.na(car_sales))
```

Removing columns with too many missing values
```{r}
car_sales <- car_sales %>%
  select(-c(Currency, Index, Vehicle_version, Vehicle_generation, CO2_emissions,
            First_registration_date,Features))
```

Filling in some missing values
```{r}

car_sales <- car_sales %>%  mutate(First_owner = case_when(
  grepl(pattern = "New", x = Condition) ~ "Yes"))

car_sales <- car_sales %>% replace_na(list(First_owner = "No"))

car_sales$First_owner <- as.factor(car_sales$First_owner)

```

Removing row with missing values
```{r}
car_sales <- car_sales %>% na.omit()
```

viewing the dataset
```{r}
glimpse(car_sales)

```

```{r}
View(car_sales)
str(car_sales)
```


Statistical summaries of dataset
```{r}
summary(car_sales)
```

The Doors_number has an outlier 55 which will be replaced by 5
```{r}
car_sales$Doors_number <- replace(car_sales$Doors_number,
                                  car_sales$Doors_number==55, 5)
```


Regression Algorithms

Simple Linear Regresion
```{r}
lr_model <- lm(Price ~ Power_HP, data = car_sales)
summary(lr_model)
```

Linear Regression with Multiple Variables
```{r}

mlg_model <- lm(Price ~ Mileage_km + Displacement_cm3 
               + Production_year + Power_HP , data = car_sales)
summary(mlg_model)
```

Classification Algorithms

Naive Bayes Classifier

Building the model
```{r}
naive_model <- naiveBayes(Condition ~ ., data = car_sales)
```

Testing the model
```{r}
naive_predict <- predict(naive_model, car_sales)
table(naive_predict, car_sales$Condition)
```

Decision Tree Classifier

Building the model
```{r}
dtree_model <- rpart(Condition ~ ., data = car_sales, method = 'class')
```


Analyzing results

```{r}
plotcp(dtree_model)
```

```{r}
summary(dtree_model)
```

Unsupervised Learning Algorithms

k-Means Clustering Algorithm

Creating a subset of integer variables from the dataset for K_means algorithm
```{r}
kcar_sales <- car_sales %>%
  select(c(Price, Production_year, Mileage_km, Power_HP, Displacement_cm3))

```

Building the model
```{r}
K_model <- kmeans(kcar_sales, 5, iter.max = 10)
```

Analysing the model
```{r}
kcar_sales <- cbind(kcar_sales, Clusternum = K_model$cluster) #adding the cluster number
                                                              #to the dataset
View(kcar_sales)
summary(K_model)
```


Hierarchical Clustering 

Spliting the data to fit the model
```{r}
hcar_sales <- kcar_sales[1:5000,]

```

Creating a distance matrix and Building the model
```{r}
h_dist <- dist(hcar_sales, method = "euclidian")  #distance matrix

h_fit <- hclust(h_dist, method = "ward")

h_groups <- cutree(h_fit, 5)

h_groups

```

Adding cluster grouping to dataset
```{r}
hcar_sales <- cbind(hcar_sales, Clusternum = h_groups)
View(hcar_sales)
```

Displaying the number of observations in each cluster
```{r}
table(h_groups)
```











